### 2017-10-31 Docs/Thesis/docs/chapter5.tex
thesis writing
README update
some updates on the thesis text

\chapter{Proof of Concepts and Validation}

@@

As first proof of concepts for our tool, we are going to use Mininet's emulated testbeds. These tests are easily implemented and reproduced, and are able to test the performance of our tool, without kernel and hardware overheads. Tests in a physical testbeds, and real network functions stays for future work.

@@

All Python scripts used to create the scenarios, the Shell Scripts used to automate the tests and capture the traffic, and the Octave scripts to perform all the calculations are available on Github\footnote{\textcolor{red}{github-link}}. To start running the tests, following the tutorial on Github, you should not take more than 10 minutes.

We will perform this testes using SIMITAR \textit{alpha} version, operation as a client on host \textit{h1}, and as a server on all other hosts. As traffic generator engine, we will use D-ITG and Iperf. The operation as a packet injector using Libtins is still unther implementation.

\section{Scalling Evaluation}

@@

\section{Packet and Flow Metrics Evaluation}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Proof of Concepts and Validation}\label{ch:validation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

As proof of concepts for our tool, we are going to use Mininet's emulated testbeds. These tests are easily implemented and reproduced, and are able to test the performance on traffic generation realism. Tests in a physical testbeds of, and network functions stays for future work.

@@

All scripts used to create the scenarios, automate the tests, and cae the traffic, and the Octave scripts to perfom all thelable at the poject github repository\footnote{\href{https://github.com/AndersonPaschoalon/ProjetoMestrado/tree/master/Tests}{https://github.com/AndersonPaschoalon/ProjetoMestrado/tree/master/Tests}}. They are organized as a set of python packages to enable easy reproductionon Github\footnote{\textcolor{red}{github-link}}. To start rub and with all depencies installed, you should not take more than 10 minutes.

We will perform this testes using SIMITAR \textit{alpha} version, operation as a client on host \textit{h1}, and as a server on all other hosts. As traffic generator engine, we will use Iperf, D-ITG, and Libtins C++ API.

\section{Simitar using Iperf and with skype-pcap}

\subsection{Single hop SDN topology}

We perform

\begin{figure}[!ht]
	\centering
	\includegraphics[scale=0.75]{figures/ch5/iperfFlowsPs.pdf}
	\caption{the caption}
	\label{fig:iperfFlowsPs}
\end{figure}

\begin{figure}[!ht]
	\centering
	\includegraphics[scale=0.75]{figures/ch5/iperfFlowCdf.pdf}
	\caption{the caption}
	\label{fig:iperfFlowCdf}
\end{figure}

\begin{figure}[!ht]
	\centering
	\includegraphics[scale=0.75]{figures/ch5/iperfBandwidth.pdf}
	\caption{the caption}
	\label{fig:iperfBandwidth}
\end{figure}

\begin{figure}[!ht]
	\centering
	\includegraphics[scale=0.75]{figures/ch5/iperfWaveletMREA.pdf}
	\caption{the caption}
	\label{fig:iperfWaveletMREA}
\end{figure}

\subsection{Tree SDN topology}

\section{Simitar using D-ITG with skype-pcap}

\section{Simitar using Libtins with skype-pcap}

\section{Simitar lanDiurnal-pcap/bigFlows-pcap}

\subsection{Iperf as packetgen tool}

\subsection{Libtins as packetgen tool}

@@
